---
title: "WS_AdvancedData_RonaresR"
author: "BJBerauer"
date: "09/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First we load packages required during the Workshop

```{r,  message=FALSE, warning=FALSE}
library(tidyverse) #l oad in the tidyverse (loading multiple packages belonging to the "tidyverse")
library(lubridate)
library(rmarkdown)
library(ggforce)
library(nlme)
library(lsmeans)
library(lme4)
library(car)
library(multcomp)
library(multcompView)
```

...and set the working directory (path-file where Workshop material was copied in)

```{r, message=FALSE, warning=FALSE, results='hide'}
getwd() # check the working directory 
#setwd() #set working directory
```


In the first section we will get started with R and commemorate basics.

We can use R as a calculator

```{r,  message=FALSE, warning=FALSE}
2-4

4/2+4 

4/(2+4) # follows mathematical rules

2*4+4/pi

pi
```

Please Note that "pi" is stored by R as an object.
We can also create objects in R 

```{r,  message=FALSE, warning=FALSE}
a <- 2
b <- 4
```

...and do calculations with them.

```{r,  message=FALSE, warning=FALSE}
a-b
b/a+b
b/(a+b)
a*b+b/pi

d <- c(2,4,6) # vector - chain of multiple "entries" [elements]
e <- c(2,5,8,11)
d+e # warning = R is doing an action, but warns you to check whats going on | coercion: R repeats the shorter object 

f <- c("can","be","letters")
#d+f # Please run this without "#" in front

```

...what happend to "d+f"? And why?

An Object is like a empty box were you can stuff in whatever you want. But there are different levels of organization of the box possible!
There are manifold classes of objects (e.g. vector, matrix, data.frame, list, tbl,...) and types of elements (e.g. numeric, character, factor, double, integer,...) within an object.

